Streaming CityJSON datasets

### 2024-05-03 paper/main.tex
Fix Gina commit

The results in Table~\ref{tab:ramtime} indicate that there is a significant benefit to using CityJSONSeq over CityJSON, at least for operations that do not require analysing or processing city objects that are close to each other.
Operations like calculating volumes, merging and subsetting files, finding city objects with specific attributes, etc.\ will all use significantly less memory and will be significantly faster.
Operations like modifying the CRS or updating the metadata would not even require to loop through the features, just to alter the first object in the file.
Operations like calculating the surface of shared walls~\citep{Agugiaro22} are however not designed for streams.

@@

Finally, because the structure of CityJSONSeq is nearly the same as that of CityJSON, in practice adding support for CityJSONSeq requires a minimum amount of effort since most of the code to parse and/or generate CityJSON objects can be reused. 
We have already added support for CityJSONSeq in a few of the open-source tools (see \url{https://www.cityjson.org/software/}) and we will continue in the future.

>>>>

The results in Table~\ref{tab:ramtime} indicate that there is a significant benefit to using CityJSONSeq over CityJSON, at least for operations that do not require analysing or processing city objects that are close to each other.
Operations like calculating volumes, merging and subsetting files, finding city objects with specific attributes, etc.\ will all use significantly less memory and will be significantly faster.
Operations like modifying the CRS or updating the metadata would not even require to loop through the features, just to alter the first object in the file.
Operations like calculating the surface of shared walls~\citep{Agugiaro22} are however not suitable for streams.

@@

Finally, because the structure of CityJSONSeq is nearly the same as that of CityJSON, in practice adding support for CityJSONSeq requires a minimum amount of effort since most of the code to parse and/or generate CityJSON objects can be reused. 
We have already added support for CityJSONSeq in a few of the open-source tools\footnote{\url{https://www.cityjson.org/software/}} and we will continue in the future.
